---
title: "Leaflet_Map"
author: "Zhengmao Zhu"
date: "August 31, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introduction
Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## Show the Position
Here is the 10 random positions near the UCONN in the map.
```{r Show the Position, comment=""}
library(leaflet)
set.seed(777)
position=data.frame(lat=runif(10, min=41.77, max=41.88),
                    lng=runif(10, min=-72.33, max=-72.22),
                    col=sample(c("red","blue","yellow"),10,replace=TRUE),
                    stringAsFactors=FALSE)
position%>%
leaflet()%>%
addTiles()%>%
addMarkers(popup=(rep("UCONN",10)),clusterOptions = markerClusterOptions())%>%
addCircleMarkers(color=position$col)%>%
addLegend(labels=LETTERS[1:3],color=c("red","blue","yellow"))
```

